`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2017-02-03 inst/manuscript/manuscript.rmd
Move the abbreviations list to above the 'Declaration' statements,as requested by editorial staff;
Renmae sections, as requested by editorial staff;

# Availablility and Implementation {-}
`flippant` has been implemented in `R` [@r_core_team_r:_2016] and is available
in The Comprehensive `R` Archive Network (CRAN). It is thus install-- and
loadable as follows from within a functional `R` environment:

@@

# Input Data and Data Processing {-}
To analyze raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information on the path to the 
fluorimeter--generated spectrum, the amount of protein reconstituted into
proteoliposomes, the assay volume before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lipids 
present (to calculate a protein to phospholipid ratio or PPR) etc. The user 
supplies this information in a spreadsheet (see below for supporting 
functionality).

@@

# Main Features {-}
## Template Generation for Data Input {-}
Supporting the user in providing the input data needed, the following function 
generates a spreadsheet program--compatible tab--delimited plain text template, 
including column names, commentary, expected data type and the default used when
omitted.

@@

## Graphic Representation of Spectral Traces {-}
In a first, graphical data analytic step of a scramblase assay--derived data 
set, fluorescent spectra or traces may be plotted in publication--appropriate
quality with acquisition time on the x-- and fluorescence intensity on the
y--axis using

@@

## Scramblase Assay Analysis {-}
Plotting protein to phospholipid ratio (PPR) against the likelihood for a given
proteoliposome to contain one or more scramblases, the PPR plot is at the heart
of the analysis of dithionite scramblase assays, allowing for the visual
comparison of specific scramblase activity between interrogated experimental
series, which may, for example, be representative of protein preparations
including mutant protein forms or crude extracts with or without depletion of a
candidate scramblase.

@@

# Case Study {-}
*Retinitis pigmentosa* is a degenerative disease of the retina, the majority of 
cases of which is linked to mutant forms of the G--protein coupled receptor 
rhodopsin [@mendes_mechanisms_2005]. Motivated by the recent discovery that 
opsin/rhodopsin has scramblase activity [@menon_opsin_2011;@goren_constitutive_2014],
we hypothesized that a class of enigmatic rhodopsin mutations, which are known
to cause *retinitis pigmentosa* yet do not display the commonly associated 
molecular phenotypes of impaired binding of retinal, folding and/or trafficking or 
transducin activation, may in fact be impacted in their scramblase activity.
This hypothesis was disproved. However, the same set of experiments pointed at a
defect in rhodopsin dimerization prior to insertion into liposomes, generating
the new hypothesis that the mutations may cause disease by interfering with the
highly ordered quarternary structure of rhodopsin in the retina 
[@ploier_dimerization_2016].

>>>>

# Implementation {-}
`flippant` has been implemented in `R` [@r_core_team_r:_2016] and is available
in The Comprehensive `R` Archive Network (CRAN). It is thus install-- and
loadable as follows from within a functional `R` environment:

@@

## Input Data and Data Processing {-}
To analyze raw data stemming from dithionite scramblase assays, `flippant` 
requires for each data point information on the path to the 
fluorimeter--generated spectrum, the amount of protein reconstituted into
proteoliposomes, the assay volume before and after addition of 
dithionite (to calculate a volume correction factor), the amount of lipids 
present (to calculate a protein to phospholipid ratio or PPR) etc. The user 
supplies this information in a spreadsheet (see below for supporting 
functionality).

@@

## Main Features {-}
### Template Generation for Data Input {-}
Supporting the user in providing the input data needed, the following function 
generates a spreadsheet program--compatible tab--delimited plain text template, 
including column names, commentary, expected data type and the default used when
omitted.

@@

### Graphic Representation of Spectral Traces {-}
In a first, graphical data analytic step of a scramblase assay--derived data 
set, fluorescent spectra or traces may be plotted in publication--appropriate
quality with acquisition time on the x-- and fluorescence intensity on the
y--axis using

@@

### Scramblase Assay Analysis {-}
Plotting protein to phospholipid ratio (PPR) against the likelihood for a given
proteoliposome to contain one or more scramblases, the PPR plot is at the heart
of the analysis of dithionite scramblase assays, allowing for the visual
comparison of specific scramblase activity between interrogated experimental
series, which may, for example, be representative of protein preparations
including mutant protein forms or crude extracts with or without depletion of a
candidate scramblase.

@@

# Results and Discussion {-}
*Retinitis pigmentosa* is a degenerative disease of the retina, the majority of 
cases of which is linked to mutant forms of the G--protein coupled receptor 
rhodopsin [@mendes_mechanisms_2005]. Motivated by the recent discovery that 
opsin/rhodopsin has scramblase activity [@menon_opsin_2011;@goren_constitutive_2014],
we hypothesized that a class of enigmatic rhodopsin mutations, which are known
to cause *retinitis pigmentosa* yet do not display the commonly associated 
molecular phenotypes of impaired binding of retinal, folding and/or trafficking or 
transducin activation, may in fact be impacted in their scramblase activity.
This hypothesis was disproved. However, the same set of experiments pointed at a
defect in rhodopsin dimerization prior to insertion into liposomes, generating
the new hypothesis that the mutations may cause disease by interfering with the
highly ordered quarternary structure of rhodopsin in the retina 
[@ploier_dimerization_2016].
